Title field: summary

### 2021-01-18 inst/examples/title.Rmd
ok

 * `r length(unique(df$title))` [unique titles](output.tables/title_accepted.csv)
 * `r sum(!is.na(df$title))` documents (`r round(100*mean(!is.na(df$title)))`%) have a title
 * [Discarded titles](output.tables/title_discarded.csv)

>>>>

 * `r length(unique(df$title))` [unique titles](output.tables/title_accepted.csv)
 * `r sum(!is.na(df$title))`/`r nrow(df)` original documents (`r round(100*mean(!is.na(df$title)), 1)`%) have data
 * `r sum(is.na(df$title))`/`r nrow(df)` documents (`r round(100*mean(is.na(df$title)), 1)`%) have missing (NA) entry
 * [Discarded titles](output.tables/title_discarded.csv) (excluding NA entries in the original data)
